Verifying Demonstrations

### 2020-07-05 paper/conclusions.tex
edits conclusion, removes example, repeats contributions (rephrased)

In this paper, we have adapted the Schnorr protocol as a
distance-bounding protocol.  It allows to construct distance-bounding
general attribute-based authentication, more general attributes than
provided by previous \ac{DB} ones.  With our contribution, Alice can
now prove more complex statements to Bob; \eg that she is older than 18 
(without revealing her actual age), has a cinema subscription which is not 
\enquote{double spent} by someone else at the same time~\cite[\eg][]{AnonPass} 
and, at the same time, Bob can be sure that Alice is not just relaying messages 
from her older sister Carol or \ac{DBMF} relaying the subscription from some 
unsuspecting stranger.

>>>>

In this paper, we have adapted the Schnorr protocol to work as a
distance-bounding protocol.  It allows us to construct distance-bounding
general attribute-based authentication, with more general attributes than
provided by previous \ac{DB} protocols.  We made and formally verified two versions of the
protocol, one that is more efficient and resistant to the attacks
leveled at \ac{DB} protocols but that assumes that more than one
bit at a time can be sent in the fast phase (as demonstrated by
\textcite{UWBPR}). We also developed a PKI scheme to generalize~\cite{UWBPR} to work for scenarios such as ours where the prover and verifier do
not trust or even know each other. The second version is a classic bit-by-bit
protocol that is not fully \ac{DBTF} resistant but otherwise fulfills
all requirements.
